Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

A {\em comparison-based $k$-SJ} algorithm for solving $(n_1, n_2, ..., n_k)$-inputs is a decision tree $\T$ defined as follows. Each internal node $u$ of $\T$ has three child nodes, referred as the {\em left}, {\em middle}, and {\em right} child, respectively. Each node is associated with an {\em instruction} of the form $(i_1, \dim_1, \lambda_1; i_2, \dim_2, \lambda_2)$.

@@

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{E}}$.} Sort all the rectangles $r \in R$ in ascending order of $\xright(r)$ (namely, the x-coordinate of the right edge of $r$). Assign the ID $i \in [R]$ to $r$ if $r$ is at the $i$-th position of the sorted list.

>>>>

A {\em comparison-based $k$-SJ} algorithm for solving $(n_1, n_2, ..., n_k)$-inputs is a decision tree $\T$ defined as follows. Each internal node $u$ of $\T$ has three child nodes, referred as the {\em left}, {\em middle}, and {\em right} child, respectively. Each node is associated with an {\em instruction} of the form $(i_1, \dim_1, \lambda_1; i_2, \dim_2, \lambda_2)$. Each leaf is associated with an {\em output}, which is defined to be a subset of $[n_1] \times [n_2] \times ... \times [n_k]$.

Given an $(n_1, n_2, ..., n_k)$-input, we execute the algorithm from the root of $\T$.

@@

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{E}}$.} Sort all the rectangles $r \in R$ in ascending order of $\xright(r)$ (namely, the x-coordinate of the right edge of $r$). To each $r \in R$, we assign an ID $i \in [R]$ if $r$ is at the $i$-th position of the sorted list.
